### 2018-04-18 Old/paper_mod_save2.tex
Moving PhD paper from Dropbox to github.

In this work, we propose a distributed progressive second price (PSP) auction in
order to maximize social utility. We show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria when all users bid their real marginal
valuation of the mobile data offered in the secondary market described in
\cite{zheng}. The P2P auction's (as in all auctions),
demand information is not known centrally, rather it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only. In this work, the proposed mechanism allows sellers submit bids to buyers
directly; there is no entity that holds a global market knowledge.

@@

The distributed PSP auction first introduced in \cite{lazar} forms a part of the
overall market based allocation model. Consider a noncooperative game
where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
amount of resource $D_i$ from a set of resources $\mcL = \lbrace 1,\cdots,L\rbrace$. Suppose
each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
seller of resource $l$,
where $p_i^l$ is the unit-price the user is willing to pay and $d_i^l$ is the
quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^l] \in \mcL \times \mcI$ (BAD NOTATION?
SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
, s_I^l]_{l\in\mcL}$ is
the profile of user $i$’s opponents. In addition, the user type now includes a
\emph{routing variable}, $r_i\in\lbrace 0, 1\rbrace^L$ to manage throughput in
an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
$i$'s path, i.e. $l(i) \in \lbrace l\in \mcL : r_i^l >0\rbrace$. 
The market now shares $L$ resources, with allocation:
$$
    \hat{D_i^l}(y,s_{-i}^l) = \bigg\lbrack D^l -
\displaystyle\sum_{p_k^l > y, k\ne i} d_k^l\bigg\rbrack^+.
$$
The market price function (MPF) of user $i$ is defined as:
% MARKET PRICE 
\begin{align*}
    \tilde{P_i}(z, s_i) &= \displaystyle\sum_{l\in\mcL}P_i^l(z_i^l,
s_{-i}^l)r_i^l \\
    = \displaystyle\sum_{l\in\mcL}&\bigg(\inf\bigg\lbrace y\ge 0 :
\hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
\end{align*}
which is interpreted as the aggragate minimum price a user bids over its route in order to obtain the
resource $z$ given the opponents’ profile $s_{−i}$. Its inverse function
$\tilde{D_i}$ is defined as follows:
% INVERSE PRICE (ALLOCATION)
\begin{align*}
    \tilde{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
\min_l\hat{D}_i^l/r_i^l\bigg) : \\
    &\tilde{P_i}(z,s_{-i}^l) < y\bigg\rbrace,
\end{align*}
which means the maximum available quantity at a bid price of $y$ given
$s_{−i}$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
as:
% ALLOCATION RULE
\begin{align*}
    \tilde{a_i}(s) &= \min_i\big\lbrace d_i^{l(i)}, \\
 &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
s_{-i}^l)\big\rbrace,
\end{align*}
\begin{align*}
    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcL}
p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
    &-\tilde{a_j}(s_i^l;s_{-i}^l)\bigg) r_i^l\bigg\rbrack,
\end{align*}
 $a_i^{l(i)}$ denotes the quantity user $i$ obtains by a bid price
$p_i^{l(i)}$ (when the
opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
$c_i^{l(i)}$. $\sum_{l\in\mcL} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
user $i$ is removed from the auction. Note that the allocation rule is modified
from \cite{lazar} according to \cite{tuffin}, so that buyers with identical unit-price
$p_i$ are not rejected.

We further modify the allocation rule in \cite{tuffin} in order to suit our
model. We argue that as there is no capacity bottleneck in our network as in
\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
take the maximum in the allocation rule. 
We propose a \emph{data allocation rule}:
{
% DATA ALLOCATION RULE
\proposition{(Data allocation rule)}
\begin{equation}\label{allocation}
    \bar{a}_i(s) = \max_i\big\lbrace d_i, \frac{d_i}{\sum_{k:p_k= p_i}d_k}
D_i(p_i,s_{-i})\big\rbrace
\end{equation}
} \\
Intuitively, this rule indicates that a seller will allocate its data to the
buyer with the highest demand that can be satisfied (within its budget). 
An allocation rule is feasible \cite{lazar} if $\forall \ s$,
$$
    \displaystyle\sum_{i\in\mcI} a_i(s) \le Q
$$
and $\forall \ i\in\mcI$,
\begin{align*}
    a_i(s) &\le d_i \\
    c_i(s) &\le p_id_i.
\end{align*}
We claim
that (\ref{allocation}) is feasible, to be shown in our analysis (SAY
BETTER).
The modified allocation rule changes the market
dynamics by adding a demand threshold to buyer behavior; the strategy is now to
submit bids to a (thresholded) subset of users, rather than submitting bids to all sellers as in \cite{lazar}, however
we still hold the assumption that data is infinitely divisibile. 
We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
opt-out buyer restricts its pool of sellers by only submitting bids to sellers
who have sufficient data to meet their requirement.
(NOTE: TAKE MAX ONLY OR NEED TO INTRODUCE
A GAP VARIABLE?), similar to \cite{zheng}. 
We intend to show that the pricing model (\ref{price}) is sufficient to attain the desirable
property of truthfullness through incentive compatibility. (MOVE THIS? NEED OWN
WORDS?) We
reason that our formulation upholds the \emph{exclusion-compensation
principle}, and is a valid progressive second price auction to the extent that buyer $i$
pays for its allocation so as to exactly cover the ``social opportunity cost" which is given by the declared willingness to pay (bids) of the users who are excluded by $i$'s
presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.

@@

We consider the set of $\mcI = \lbrace 1, \cdots, I\rbrace$ users who purchase or sell
data from other users. A buyer is matched with sellers who enough leftover data
to satisfy thier demand, and will submit bids in order to maximize thier (private) valuation.
A user's identity $i \in \mcI$ as a subscript indicates that the user
is a buyer, and a superscript indicates the seller.
Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. (STILL TRUE?) Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, then this means that
the user has the exact amout of data they require, or that seller $j$ does not have
enough data to satisfy the buyer's demand, and we simply set $s^j_i = (0, 0)$.
A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
quantity $d_j^j$ , with a reserve unit price of $p_j^j$ . In other words, when the subscript and
superscript are the same, the bid is understood as an offer in the secondary
market; we assume that data is a unary resource belonging to the seller, and
therefore can identify the data (for sale) with the identity of the user.
With this restriction, we note that since $i$ is not a seller, $d_i^i = 0$ and
$a^i = 0$. We may simplify the notation so that $s_j^j = (d_j^j, p_j^j) = s^j = (d^j, p^j)$.

@@

% OPT-OUT BUYER
We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
function as in \cite{semret},
\begin{equation}\label{opt-utility}
    u_i = \theta_i \circ e_i(a) - \displaystyle\sum_j c_i^j,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation (FUTURE
WORK) that user
$i$ finds a matching seller $j$. An opt-out buyer's valuation
depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market.

Suppose the total amount of seller $j$'s data on the network at the instance that
user $i$ joins the auction is $\bar{b}^j$. For the service to function as desired,
the data transfer from each seller cannot exceed the total amount they have available,
i.e. $a_i^j \le \bar{b}^j$. (CHECK THE MATH!) This will hold simultaneously for each $j \in
\mcL_i$ if and only if $\bar{b}^j \ge \max_j \ a_i^j \vs_i^j = e_i(a)$.
(TERRIBLE NONSENSE) Thus $e_i(a)$
lower-bounds the amount of data that each seller $j$ has in an auction.
We define the set of \emph{qualifying sellers} for buyer $i$,
% QUALIFYING SELLERS
\begin{equation}\label{sellers}
     \mcL_i = \lbrace j \in \mcI : \bar{b}^j \ge e_i(a) \rbrace,
\end{equation}
and denote the set of buyers who submit bids to $j$ as $\mcI^j = \lbrace i\in\mcI : j \in
\mcL_i\rbrace.$

Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
rational (utility-maximizing) buyer will set $s_i^j = 0$, i.e. they will not
place a bid, as in \cite{zheng}.

Buyer $i$'s valuation may now be interpreted as a unit valuation $\theta_i$, scaled
by a function of quantity desired from the market. 
We define, in addition to the valuation and budget of user $i$, a generic
\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
following (novel) strategy,
{
\theorem{(Opt-out buyer strategy)}\label{strategy}
Define, for any allocation $a$,
% OPT-OUT FUNCTION
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
    e_i^j(a) \triangleq a_i^j\vs_i^j,
\end{equation}
and let
\begin{equation}
    e_i(a) \triangleq \min\bigg(\max_j e_i^j(a), \delta\bigg),
\end{equation}
where $\delta = \max_k d_k$ where $k\in \mcL_i$ and $s_i = (\delta,
\theta'(\delta)) \in S_i(s_{-i})$, where 
$$
    S_i(s_{-i}) = \bigg\lbrace s_i : \displaystyle\sum_j c_i^j(s_i;s_{-i}) \le b_i\bigg\rbrace,
$$
is given as in \cite{lazar} and $b_i$ is user $i$'s budget. In other words, the
buyer will always make a maximum feasible bid (WHY IS IT FEASIBLE? BETTER MIN
AND STAY IN AUCTION? PRICE OR QUANTITY?). 
Under this rule, the secondary market described in \cite{zheng} converges to a $\epsilon$-Nash equilibrium.
}\\
\textbf{Proof:}
We will prove the theorem by asserting that our formulation upholds the VGC
mechanism that is given in the properties of modern PSP. Namely,
\begin{itemize}
    \item Incentive compatibility
    \item Efficiency 
    \item Convergence
\end{itemize}

The seller, in our analysis, is an extension of the buyer, where the valuation
$\theta^j$ is dependent on the buyers, we will assume that buyers and sellers
are separated (a seller does not also buy data and vice versa).

The natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with opt-out value
$e_i(a)$ for each buyer $i$ that has $j$ in its set of qualified buyers
$\mcI^j$. Note that we have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
participate in any auction. Additionally, as the
value of the secondary market is its ability to fufill the data demands of its
users, we determine the
valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
and the form of (\ref{opt-out}) is justified. 
\iffalse
We may now define the maximum
quantity of \emph{data} at bid price $y$ given $s_{-i}$:
% NEW DEMAND
\begin{align}
\begin{split}
    \bar{D}_i(y,s_{-i}) &= \max_j \bigg(D_i^j(y,s_{-i}^j)\ \circ\ e_i\bigg)\\
    &= \max_j\bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\vs_k^j\bigg\rbrack^+.
\end{split}
\end{align}
\fi
(MOVE?)
Define, for a buyer $i$,
$$
    \ell_i =\min_{n\in\mcI} \bigg( \argmax_{\mcL_i' \subset \mcL_i, \vert\mcL_i'\vert =
n}\sum_{j\in\mcL_i'} d^j\bigg),
$$
and
\begin{equation}\label{minset}
    \bar{\mcL_i} = \bigg\lbrace j \in  \ell_i:
\displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
\end{equation} 
where $\bar{\mcL_i} \subset \mcL_i$ is the
minimal subset of sellers (which may be empty or unary) whose data can sum to \emph{exactly}
(DO I WANT EXACTLY? ... YES) the demand $d_i$.
We note that as we assume $\forall \ j \in \mcL_i, d^j \ge
d_i$, the subset definition is expressed here for notational ease.
Additionally, we define, for a seller $j$,
$$
    \beta^j = \bigg\lbrace i\in\bar\mcI^j: \sum_i
d_i^j \le \bar{b}^j \bigg\rbrace,
$$
and so, similarly to (\ref{minset}),
\begin{equation}\label{maxset}
    \bar{\mcI}^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
\end{equation}
as the maximum subset of buyers $\in\mcI^j$ that $j$ can satisfy with budget
$\bar{b}^j$. The set $\beta^j$ is computed at each bidding iteration,
i.e., for $\tau >0$, 
\begin{align*}
    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\bar\mcI^j: \sum_i
        d_i^j \le \bar{b}^j \bigg\rbrace, \\
    \text{where}&\\
    \bar{b}^j &= b_j - \sum_{t\in
\tau} d_i^{j(t)}
\end{align*}
and $b^j$ is $j$'s original budget.

\subsection{Data Auction Mechanism}
We may now proceed to formally define the PSP auction.
The market price function (MPF) for a user in the secondary market
can now be described as follows:
% NEW MARKET PRICE
\begin{align}
\begin{split}
    \bar{P}_i(z, s_i) &= \displaystyle\sum_{j\in\bar\mcL_i}P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\bar\mcL_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
\end{split}
\end{align}
where
\begin{align}
\begin{split}
    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\vs_k^j\bigg\rbrack^+,
\end{split}
\end{align}
which is interpreted as the minimum bid price, as in \cite{lazar}.
The inverse function
$\bar{D}_i$ is defined as
\begin{align}
\begin{split}
    \bar{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
\sum_{j\in\bar\mcL_i} \bar{D}_i^j \bigg) : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace.
\end{split}
\end{align}
The rules defined above describe the mechanism for the PSP auction given in
\cite{lazar}, however, in order to apply PSP to the data-sharing secondary market described in
\cite{zheng} the idea of a ``route" is repurposed. We claim that in the
data-sharing model, it is not necessary to bid on a minimal route, and that our
formulation not only holds the desired VCG qualities, but minimizes the message
space and auction duration, resulting in a faster convergence time than the
classic throughput problem (EEEK!).

@@

>>>>

In this work, we propose a distributed progressive second price (PSP) auction in
order to maximize social utility. We show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria when all users bid their real marginal
valuation of the mobile data offered in the secondary market described in
\cite{zheng}. The PSP auction's (as in all auctions),
demand information is not known centrally, rather it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only. In this work, the proposed mechanism allows sellers submit bids to buyers
directly; there is no entity that holds a global market knowledge.

@@

The distributed PSP auction first introduced in \cite{lazar} forms a part of the
overall market based allocation model. Consider a noncooperative game
where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
amount of resource $D_i$ from a set of resources $\mcL = \lbrace 1,\cdots,L\rbrace$. Suppose
each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
seller of resource $l$,
where $p_i^l$ is the unit-price the user is willing to pay and $d_i^l$ is the
quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^l] \in \mcL \times \mcI$ (BAD NOTATION?
SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
, s_I^l]_{l\in\mcL}$ is
the profile of user $i$’s opponents. In addition, the user type now includes a
\emph{routing variable}, $r_i\in\lbrace 0, 1\rbrace^L$ to manage throughput in
an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
$i$'s path, i.e. $l(i) \in \lbrace l\in \mcL : r_i^l >0\rbrace$. 
The market now shares $L$ resources, with allocation:
$$
    \hat{D_i^l}(y,s_{-i}^l) = \bigg\lbrack D^l -
\displaystyle\sum_{p_k^l > y, k\ne i} d_k^l\bigg\rbrack^+.
$$
The market price function (MPF) of user $i$ is defined as:
% MARKET PRICE 
\begin{align*}
    \tilde{P_i}(z, s_i) &= \displaystyle\sum_{l\in\mcL}P_i^l(z_i^l,
s_{-i}^l)r_i^l \\
    = \displaystyle\sum_{l\in\mcL}&\bigg(\inf\bigg\lbrace y\ge 0 :
\hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
\end{align*}
which is interpreted as the aggragate minimum price a user bids over its route in order to obtain the
resource $z$ given the opponents’ profile $s_{−i}$. Its inverse function
$\tilde{D_i}$ is defined as follows:
% INVERSE PRICE (ALLOCATION)
\begin{align*}
    \tilde{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
\min_l\hat{D}_i^l/r_i^l\bigg) : \\
    &\tilde{P_i}(z,s_{-i}^l) < y\bigg\rbrace,
\end{align*}
which means the maximum available quantity at a bid price of $y$ given
$s_{−i}$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
as:
% ALLOCATION RULE
\begin{align*}
    \tilde{a_i}(s) &= \min\big\lbrace d_i^{l(i)}, \\
 &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
s_{-i}^l)\big\rbrace,
\end{align*}
\begin{align*}
    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcL}
p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
    &-\tilde{a_j}(s_i^l;s_{-i}^l)\bigg) r_i^l\bigg\rbrack,
\end{align*}
 $a_i^{l(i)}$ denotes the quantity user $i$ obtains by a bid price
$p_i^{l(i)}$ (when the
opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
$c_i^{l(i)}$. $\sum_{l\in\mcL} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
user $i$ is removed from the auction. Note that the allocation rule is modified
from \cite{lazar} according to \cite{tuffin}, so that buyers with identical unit-price
$p_i$ are not rejected.

An allocation rule is feasible \cite{lazar} if $\forall \ s$,
$$
    \displaystyle\sum_{i\in\mcI} a_i(s) \le Q
$$
and $\forall \ i\in\mcI$,
\begin{align*}
    a_i(s) &\le d_i \\
    c_i(s) &\le p_id_i.
\end{align*}

We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
opt-out buyer restricts its pool of sellers by only submitting bids to sellers
who have sufficient data to meet their requirement.
(NOTE: TAKE MAX ONLY OR NEED TO INTRODUCE
A GAP VARIABLE?), similar to \cite{zheng}. 
We intend to show that the pricing model (\ref{price}) is sufficient to attain the desirable
property of truthfullness through incentive compatibility. (MOVE THIS? NEED OWN
WORDS?) We
reason that our formulation upholds the \emph{exclusion-compensation
principle}, and is a valid progressive second price auction to the extent that buyer $i$
pays for its allocation so as to exactly cover the ``social opportunity cost" which is given by the declared willingness to pay (bids) of the users who are excluded by $i$'s
presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.

@@

We consider the set of $\mcI = \lbrace 1, \cdots, I\rbrace$ users who purchase or sell
data from other users. A buyer submits bids directly to sellers who enough leftover data
to satisfy their demand, and will submit bids in order to maximize thier
(private) valuation. We assume (SUPPOSE?) that the public information in the
secondary market consists of a set of offers that are published by users
wishing to sell their data overage. 
A user's identity $i \in \mcI$ as a subscript indicates that the user
is a buyer, and a superscript indicates the seller.
Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. (STILL TRUE?) Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, then this means that
the user has the exact amout of data they require, or that seller $j$ does not have
enough data to satisfy the buyer's demand, and we simply set $s^j_i = (0, 0)$.
A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
quantity $d_j^j$ , with a reserve unit price of $p_j^j$ . In other words, when the subscript and
superscript are the same, the bid is understood as an offer in the secondary
market; we assume that data is a unary resource belonging to the seller, and
therefore can identify the data (for sale) with the identity of the user.
With this restriction, we note that since $i$ is not a seller, $d_i^i = 0$ and
$a^i = 0$. We may simplify the notation so that $s_j^j = (d_j^j, p_j^j) = s^j =
(d^j, p^j)$. In our current formulation, we do not allow a seller to submit
multiple bids $s^j$ (FUTURE WORK).

@@

% OPT-OUT BUYER
We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
function as in \cite{semret},
\begin{equation}\label{opt-utility}
    u_i = \theta_i \circ e_i(a) - \displaystyle\sum_j c_i^j,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation 
(???? BAD) that user
$i$ finds a matching seller $j$. An opt-out buyer's valuation
depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market.

Suppose the total amount of seller $j$'s data on the network at the instance that
user $i$ joins the auction is $\bar{b}^j$. 
The data transfer from each seller cannot exceed the total amount they have available,
i.e. $a_i^j \le \bar{b}^j$. (CHECK THE MATH!) This will hold simultaneously for each $i \in
\mcI$ if and only if $\bar{b}^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
restricted to subset of buyers $\in\mcI$.
We define the set of \emph{qualifying sellers} for buyer $i$,
% QUALIFYING SELLERS
\begin{equation}\label{sellers}
     \mcL_i = \lbrace j \in \mcI : \bar{b}^j \ge d_i \rbrace,
\end{equation}
and denote the set of buyers who submit bids to $j$ as $\mcI^j = \lbrace i\in\mcI : j \in
\mcL_i\rbrace.$

Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
rational (utility-maximizing) buyer will set $s_i^j = 0$, i.e. they will not
place a bid, as in \cite{zheng}. The seller, in our analysis, is an extension of the buyer, where the valuation
$\theta^j$ is dependent on the buyers, we will assume that buyers and sellers
are separated (a seller does not also buy data and vice versa).

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that many sellers will come close to using their
entire data cap, and only sell the fractional overage. Additionally, a buyer
will most likely not purchase fractional amounts of data, as this would incur
additional bid fees (...AND). In this case, we
determine that a buyer must coordinate their bids among multiple sellers. (SAY
MORE?) To aid in our analysis, we define, for a buyer $i$,
% MIN SET
$$
    \ell_i =\argmax_{\mcL_i' \subset \mcL_i, \vert\mcL_i'\vert =
n}\sum_{j\in\mcL_i'} d^j,
$$
where $n\in\mcI$ is chosen so that
\begin{equation}\label{minset}
    \bar{\mcL_i} = \bigg\lbrace j \in  \ell_i:
\displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
\end{equation} 
where $\bar{\mcL_i} \subset \mcL_i$ is the
minimal subset of sellers (which may be empty or unary) whose data can sum to \emph{exactly}
(DO I WANT EXACTLY? ... YES) the demand $d_i$.
We note that as we assume $\forall \ j \in \mcL_i, d^j \ge
d_i$, the subset definition is expressed here for notational ease.
Additionally, we define, for a seller $j$,
$$
    \beta^j = \bigg\lbrace i\in\bar\mcI^j: 
d_i \le \bar{b}^j \bigg\rbrace,
$$
and so, similarly to (\ref{minset}),
% MAX SET
\begin{equation}\label{maxset}
    \bar{\mcI}^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
\end{equation}
as the maximum subset of buyers $\in\mcI^j$ that $j$ can satisfy with budget
$\bar{b}^j$. The set $\beta^j$ is computed at each bidding iteration,
i.e., for $\tau >0$, 
\begin{align*}
    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\bar\mcI^j: 
        d_i \le \bar{b}^j \bigg\rbrace, \\
    \text{where}&\\
    \bar{b}^j &= b_j - \sum_{t\in
\tau} d_i^{j(t)}
\end{align*}
and $b^j$ is $j$'s original budget.

Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, scaled
by a function of quantity desired from the market. 
We define, in addition to the valuation and budget of user $i$, a generic
\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
following (novel) strategy,
{
\theorem{(Opt-out buyer strategy)}\label{strategy}
Define, for any allocation $a$,
% OPT-OUT STRATEGY
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
\end{equation}
and let
\begin{equation}
    e_i(a) \triangleq \min_j\bigg(e_i^j(a)\bigg),
\end{equation}
(REWORD) In other words, the
buyer will always make a maximum feasible bid (WHY IS IT FEASIBLE? BETTER MIN
AND STAY IN AUCTION? PRICE OR QUANTITY?). 
Under this rule, the secondary market described in \cite{zheng} converges to a $\epsilon$-Nash equilibrium.
}\\
\textbf{Proof:}
We will prove the theorem by asserting that our formulation upholds the VGC
mechanism that is given in the properties of modern PSP. Namely,
\begin{itemize}
    \item Incentive compatibility
    \item Efficiency 
    \item Convergence
\end{itemize}

The natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with opt-out value
$e_i(a)$ for each buyer $i$ that has $j$ in its set of qualified buyers
$\mcI^j$. Note that we have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
participate in any auction. Additionally, as the
value of the secondary market is its ability to fufill the data demands of its
users, we determine the
valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
and the form of (\ref{opt-out}) is justified.

\subsection{Data Auction Mechanism}
We may now proceed to formally define the PSP auction.
The market price function (MPF) for a user in the secondary market
can now be described as follows:
% NEW MARKET PRICE
\begin{align}
\begin{split}
    \bar{P}_i(z, s_i) &= \displaystyle\sum_{j\in\bar\mcL_i}P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\bar\mcL_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
\end{split}
\end{align}
where
\begin{align}
\begin{split}
    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+\vs_i^j,
\end{split}
\end{align}
and is interpreted as the minimum bid price, as in \cite{lazar}.
The inverse function
$\bar{D}_i$ is defined as
\begin{align}
\begin{split}
    \bar{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
\sum_{j\in\bar\mcL_i} \bar{D}_i^j \bigg) : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace.
\end{split}
\end{align}
We may interpret $\bar{D}_i(y, s_i)$ as the maximum quantity provided by the subset
$\bar\mcL_i$ at a bid price of $y$ given $s_{i}$.

The rules defined above describe the mechanism for the PSP auction given in
\cite{lazar}, however, in order to apply PSP to the data-sharing secondary market described in
\cite{zheng} the idea of a ``route" is repurposed. We claim that in the
data-sharing model, it is not necessary to bid on a minimal route, and that our
formulation not only holds the desired VCG qualities, but minimizes the message
space and auction duration, resulting in a faster convergence time than the
classic throughput problem (EEEK!).

@@

In order to complete our formulation, we argue that as there is no capacity bottleneck in our network as in
\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
take the maximum in the allocation rule. 
We propose a \emph{data allocation rule}:
{
% DATA ALLOCATION RULE
\proposition{(Data allocation rule)}
Given an auction of infinitely divisible data $j$, where user $j$ is the
auctioneer, the data allocation rule is given as,
\begin{equation}\label{allocation}
    \bar{a}_i^j(s) = \max_i\big\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
p_i^j}d_k^j}
\bar{D}_i^j(p_i^j,s_{-i}^j)\big\rbrace
\end{equation}
where $i\in\bar\mcI^j$.
} 
\textbf{Proof}:
Intuitively, this rule indicates that a seller will allocate its data to the
buyer with the highest demand that can be satisfied (within its budget). 
(\ref{allocation}) is feasible by (\ref{quantity}) and (\ref{budget}), in that
$$
    \displaystyle\sum_{i\in\mcI} a_i(s) \le \displaystyle\sum_{i\in\mcI} e_i(a)
\le \sum_{j\in\mcI} b^j = \mathcal{D},
$$
where $\mathcal{D} = \sum_{j\in\mcI} d^j$ is the total amount data for sale in the secondary market.
As the buyers ``control" the secondary market via their individual data demands,
$\forall \ i\in\mcI$,
\begin{align*}
    a_i(s) &\le e_i(a) \le d_i \\
    c_i(s) &\le p_id_i.
\end{align*}
where $c_i(s)$ remains unchanged from \cite{lazar}. (FINISH!)
